---
title: "depigner: package of utilities for _pignas_."
output: github_document
bibliography: 'bib/doc-pkg.bib'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r include = FALSE}
knitr::opts_chunk$set(
  eval     = FALSE,
  collapse = TRUE,
  comment  = "#>"
)
library(magrittr)
library(pander)
```

## Overview
This package collect usefull function frequently used at the Unit of
Biostatistics, Epidemiology and Public Health of the Department of Cardiac,
Thoracic and Vascular sciences at the university of Padova.


## Install and usage
To install the development version (the only one for the moment) from GitHub:

```{r}
# install.packages("devtools")
devtools::install_github("CorradoLanera/depigner")
```

Once the package is installed, simply load it
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, eval = TRUE}
library(depigner)
```

## Provided function

- **`summary_interact()`**: produce a data frame of OR (with the corresponding
  CI95%) for the interactions between different combination of a continuous
  variable (for which it is possible to define the reference and the target
  values) and (every or a selection of levels of) a categorical one in a
  logistic model provided by `lrm()` (from the `rms` package [@R-rms]).
```{r message=FALSE, warning=FALSE, eval = TRUE, include = FALSE}
library(rms)
  options(datadist = 'dd')

data('transplant')
transplant <- transplant[transplant[['event']] != 'censored', , drop = FALSE]
dd <- datadist(transplant)

lrm_mod <- lrm(event ~ rcs(age, 3)*(sex + abo) + rcs(year, 3),
  data = transplant
)
```
```{r echo=FALSE, message=FALSE, warning=FALSE, eval = TRUE}
summary_interact(lrm_mod, age, abo) %>% pander
```
  

## Provided data
None at the moment.

## Feature request
If you need some more features, please open an issue on
[github](https://github.com/CorradoLanera/depigner/issues).


## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example) on [github](https://github.com/CorradoLanera/depigner/issues).


<!--=========================================================================-->

## Reference

```{r bib, include=FALSE, eval = TRUE}
# create a bib file for the R packages used in this document
knitr::write_bib(
  x    = c('rms'),
  file = 'bib/doc-pkg.bib'
)
```
